Evolution of solar wind discontinuities in the inner heliosphere

### 2024-01-31 index.qmd
update

## Events

2018∕10∕24 PSP Earth

@@

### 2019∕04∕07

``` txt
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

@@

![](images/paste-18.png)

::: {.column-page layout-nrow="1"}
![](images/paste-16.png)

![](images/paste-17.png)
:::

## Trange: Encounter 8

>>>>

# Events

## 2018-10-24 PSP Earth

@@

## 2019-04-07
``` txt
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

@@

::: {.column-page layout-nrow="1"}

![PSP observation](images/paste-18.png)

![ACE observation](images/paste-16.png)

![ACE observation (continued)](images/paste-17.png)
:::

# Trange: Encounter 8
